Supplement to Automatic Matching of Bullet Lands

### 2015-12-31 imaging-supplement.Rnw
including the modified functions into the old ones.

new_get_bullet <- function(path, x = 243.75, bullet = NULL) {
  if (is.null(bullet)) bullet <- read.x3p(path)
  dbr111 <- fortify_x3p(bullet)

  pickx <- dbr111$x[which.min(abs(x - unique(dbr111$x)))]

  dbr111.fixx <- dbr111[dbr111$x == pickx,]

  return(dbr111.fixx)
}

@@

  list_of_fits <- lapply(crosscuts, function(x) {
    br111 <- new_get_bullet(path = NULL, x = x, bullet = bullet)
    br111.groove <- get_grooves(br111)
    fit_loess(br111, br111.groove)$resid$data
  })
  lof <- list_of_fits %>% bind_rows

@@

\newpage
\section{One-on-one comparison of Hamby study}\label{supp:extended}
\hh{
add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$).  What would be fun, would be to show all of the aligned signatures for all ten barrels. (moved to supplement)
}
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}

>>>>

@@

  list_of_fits <- lapply(crosscuts, function(x) {
    br111 <- get_crosscut(path = NULL, x = x, bullet = bullet)
    br111.groove <- get_grooves(br111)
    fit_loess(br111, br111.groove)$resid$data
  })
  lof <- list_of_fits %>% bind_rows

@@

\newpage
\section{One-on-one comparison of Hamby study}\label{supp:extended}
\hh{
add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$).  
}
\hh{Show aligned signatures for all ten barrels. }
<<aligned, echo=FALSE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br. Bullet ", "", mm$value)

@
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}
